Rigidity of Expectations: Additional Evidence from Density Forecasts of the Inflation by Professionals and Households

### 2019-12-01 paper/InfVar.tex
seperately back up the paper draft latex until before incorporating SV and structural estimations. Then started working on InfVar.tex with new abstract.

	\begin{abstract}
		Surveys on density forecasts of macroeconomic variables that are not available until recently provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation as well as other stylized facts across economists and households.  Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific rigidity using uncertainty as a next step of the analysis.

	\end{abstract}

@@

	Individual forecast error $FE_{i,t+h|t}$ is the difference of individual forecast at time $t$ and ex post realized value of $y_{t+h}$.

@@

	\begin{eqnarray}\label{NoPastInfFE}
		\overline{FE}^{*}_{i,t+h|t} = \sum^{h}_{k=1} \rho^k \omega_{t+k}
	\end{eqnarray}

@@

	It is easy to show that the average forecast errors are serially correlated (Equation \ref{FESEPop}). For double-checking, setting $\lambda=1$, SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully responds to newly realized shocks at time $t$.

	\begin{eqnarray}\label{FESEPop}
		\begin{aligned}
			\overline{FE}_{t+h|t}  = (1-\lambda) \overline {FE}_{t+h|t-1} + \lambda \rho^h \omega_t 
		\end{aligned}
	\end{eqnarray}

@@

	\bibliographystyle{apalike}
	\bibliography{TestingExpectationTheories}

>>>>

	\begin{abstract}
	Density forecasts of macroeconomic variables provide one additional moment restriction, uncertainty, for testing and exploring the implications of theories about how people form expectations differently from full-information rationality benchmark. This paper first documents the persistent dispersion in inflation uncertainty of professionals and households, and how it conveys different information from the widely used proxies to uncertainty such as cross-sectional disagreement and forecast errors. Second, utilizing the panel data structure of both surveys, I provide additional reduced-form test results as well as structural estimates for each particular theory of ``irrational expectation'' by jointly accounting for its predictions for different moments. This is a natural extension of \citet{coibion2012can}, which examines different moments separately. Also, motivated by the time-varying pattern of the uncertainty observed from the surveys, I extend their work to allow for an alternative inflation process featuring stochastic volatility. These extensions allow me to match the joint dynamics of inflation and forecast moments in a better degree of fitness than the in baseline setting. It also illustrates how incorporating higher moments from survey data helps understand both the expectation formation mechanisms and inflation dynamics.   
	\end{abstract}

@@

	Individual forecast error $FE_{i,t+h|t}$ is the difference of individual forecast at time $t$ and ex post realized value of $y_{t+h}$.  By definition. positive(negataive) forecast errors mean overpredict (underpredict) the variables.

@@

	\begin{eqnarray}\label{NoPastInfFE}
		\overline{FE}^{*}_{i,t+h|t} = - \sum^{h}_{k=1} \rho^k \omega_{t+k}
	\end{eqnarray}

@@

	It is easy to show that the average forecast errors are serially correlated (Equation \ref{FESEPop}). For double-checking, setting $\lambda=1$, SE collapses to FIRE, as seen in Equation \ref{NoPastInfFE}, in which there is no serial correlation between forecast errors and it fully responds to newly realized shocks at time $t$.

	\begin{eqnarray}\label{FESEPop}
		\begin{aligned}
			\overline{FE}_{t+h|t}  = (1-\lambda) \overline {FE}_{t+h|t-1} - \lambda \sum^{h}_{k=1}\rho^k \omega_{t+k} 
		\end{aligned}
	\end{eqnarray}

@@

	\bibliographystyle{apalike}
	\bibliography{InfVar}
